\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization \thanks{Matthew Gardner, Andrew McNabb, and Kevin Seppi are with the Department of Computer Science, Brigham Young University, 3361 TMCB, Provo, UT 84602 (phone: 801-422-8717; email: \{mjg82,a,k\}@cs.byu.edu).}

### 2010-04-08 honors_thesis/journal_paper/paper.tex
Some minor fixes to make things work better

To solve this problem, we propose a method for performing two iterations of PSO
at the same time in parallel that we call speculative evaluation.  The name
comes from an analogy to speculative execution (also known as branch
prediction) techniques commonly used in processors.  Modern processors, when
faced with a branch on which they must wait (e.g. a memory cache miss), guess
which way the branch will go and start executing, being careful not to make
changes that can not be undone.  If the processor guesses right, execution is
much farther ahead than if it had just idly waited on the memory reference.  If
it guesses wrong, execution restarts where it would have been anyway.

@@

\bibliographystyle{unsrt}
\bibliography{%
../../../bib/aml/bib,%
../../../bib/pso/general/bib,%
../../../bib/pso/parallel/bib,%
../../../bib/pso/topology/bib,%
../../../bib/sim-anneal/parallel/bib,%
../../../bib/ga/bib,%
}

>>>>

To solve this problem, we propose a method for performing two iterations of PSO
at the same time in parallel that we call speculative evaluation.  The name
comes from an analogy to speculative execution (also known as branch
prediction) techniques commonly used in processors.  Modern processors, when
faced with a branch on which they must wait (e.g. a memory cache miss), guess
which way the branch will go and start executing, being careful not to make
changes that cannot be undone.  If the processor guesses right, execution is
much farther ahead than if it had just idly waited on the memory reference.  If
it guesses wrong, execution restarts where it would have been anyway.

@@

\bibliographystyle{unsrt}
\bibliography{%
../../../bib/aml/bib,%
../../../bib/pso/general/bib,%
../../../bib/pso/parallel/bib,%
../../../bib/pso/topology/bib,%
../../../bib/sim-anneal/parallel/bib,%
../../../bib/ga/bib%
}
